\section{Model Selection}

At the very beginning, we tried various models and picked the model with 
the highest prediction accuracy, which is XGBoost. The steps to train and test
each model are as following:
\begin{enumerate}
    \item We picked the 2015 Regular Season data and 2016 Regular Season data
    from www.basketball-reference.com/ as training and testing data respectively.

    \item We trained the model based on the 2015 Regular Season data, with 
	    parameters selected from 10-fold cross-validation. For training the
	    model, we treated each game as one observation. And for each game,
	    we used the performance of both teams, say Team A and Team B, and
	    other game related data (such as the players’ information and whether
	    the game is played at Team A’s home field) as features.
	\item Based on our model, we predicted the outcome of each game on 
	    2016 Regular Season. For each team, we found all the historical games 
	    it played and used dynamic moving average of the history data as the measure
	    of performance of one team. For predicting the results for each game,
	    knowing which two teams will play, we combined the historical performance 
	    of the two teams and added other information as test features. Once a
	    game finished, we updated the historical performance of both
	    participated teams, and continued the process until the last game.
	\item Following the above procedure, we finally found that the XGBoost had 
	    the best prediction accuracy, which was 70.2\%.
\end{enumerate}



